\renewcommand*{\hbPartCover}{assets/ext/lagiacrus}
\renewcommand*{\hbPartSubcover}{assets/ext/lagiacrus2}
\part{Monsters}


\chapter{Monster Listings}
The world of \MH{} is teeming with, you guessed it, monsters. The term "Monster" generally refers to any animal, even domesticated ones, with the possible exception of some very cute kittens, and poogies.

\paragraph{Creature Types.} The creature types of \DND{} are aberration, beast, celestial, construct, dragon, elemental, fey, fiend, giant, humanoid, monstrosity, ooze, plant and undead. Most of these are not applicable to \MH{}, so we are using different ones to balance out the preferred enemy of the ranger. The \MH{} creature types are lynian, herbivore, neopteron, temnoceran, bird wyvern, flying wyvern, piscine wyvern, carapaceon, amphibian, fanged beast, leviathan, snake wyvern, brute wyvern, fanged wyvern and elder dragon. That's too many and some of these categories have only a single entry.

Therefor, the creature types that we are using are: Beast, bird wyvern, flying wyvern, brute wyvern, leviathan and elder dragon. The following sections will list the monsters sorted by these categories.

\paragraph{But what about the undead?} Some classes, particularly the cleric, lose out on quite a few abilities if there are no undead. However, don't discard those features just yet, there might just be something that comes quite close enough for those abilities to work\ldots

\paragraph{Monster Ratings.} Officially, the monsters of \MH{} have star ratings from one star to six stars (with some exceptions like Alatreon having eight). Quests, however, are rated with one to ten stars and require a hunter rank of at least the amount of stars the quest has to undertake. \DND{} ranks monsters by challenge rating, where a monster of a certain challenge rating is supposed to be a challenge to a party of that level (this does \emph{not} work in practice, by the way). Here, I will rank the monsters with one through ten stars to differentiate the levels of \MH{} some more. However, this is not a precise science and as a DM, you are more than welcome to assign a different level to one of the monsters and have your party face it at an earlier or later time. Just like in \emph{Dragonball}, \emph{power levels are bullshit}.

Without further ado, on to the monsters.

\begin{hbFancyWideTable}{Monster By Rating}{RYYYYY}
\textbf{Rating} & \textbf{Beasts} & \textbf{Brute Wyverns} & \textbf{Bird Wyverns} & \textbf{Flying Wyverns} & \textbf{Leviathans}\\
No Stars & Altaroth, Anteka, Bnahabra, Moofah & Aptonoth, Larinoth & Gargwa & \hbNone &  Fish\\
One Star & \hbNone & \hbNone & Jaggi, Velociprey & \hbNone & Delex, Ludroth\\
Two Stars & Arzuros & \hbNone & Velocidrome & \hbNone & \hbNone\\
Three Stars & \hbNone & \hbNone & \hbNone & \hbNone & Plesioth\\
Four Stars & \hbNone & \hbNone & \hbNone & Khezu, Rathian & \hbNone\\
Five Stars & \hbNone & \hbNone & \hbNone & \hbNone & \hbNone\\
Six Stars & \hbNone & \hbNone & \hbNone & Tigrex & \hbNone\\
Seven Stars & \hbNone & Deviljho & \hbNone & \hbNone & \hbNone\\
\end{hbFancyWideTable}

\let\svaddcontentsline\addcontentsline
\renewcommand\addcontentsline[3]{%
  \ifthenelse{\equal{#1}{lof}}{}%
  {\ifthenelse{\equal{#1}{lot}}{}{\svaddcontentsline{#1}{#2}{#3}}}}

\section{Beasts}
Beasts is a term referring to mammals of every kind, insects as well as some birds.

\monsterheader{assets/ext/icons/altaroth}{Altaroth}{\FiveStarOpen}{No Stars}
\textit{Insects that widely inhabit many areas. They absorb fruit, mushrooms, and honey, and then carry them back to their nest. Materials can thus be collected from their swollen abdomens, whose color is related to what they're carrying.}
\subsubsection{Physiology \& Ecology}
Altaroth are green ant-like insects growing up to 120cm long. Their appearance is characterised by a thin waist, a swollen, brightly colored abdomen and a large yellow crest which looks rather like a bonnet. Altaroth eat plants, mushrooms, nuts and sometimes roots, which they break down using their long mandibles and store in their abdomens, which can swell up to several times its normal size. When it does, the color of the material they have ingested is visible, giving the abdomen a varying bright coloring. In addition to their mandibles, they rely on a stinger for defense, as well as shooting corrosive formic acid from their stomach.

Altaroth occur in most regions and climates, they can even be found in arctic and desert areas, though there they keep to sheltered areas. There is some regional variety in the size and shape of the crest. In addition, there are two types of Altaroth, depending on their role within the hive: Soldier and worker. Soldiers have bigger crests and stronger mandibles but cannot store nutrients like workers can. However, even soldier Altaroth are hardly a threat to humanoids, as they are quite weak and their exoskeleton is considerably weaker than that of other insects.

\subsubsection{Behaviour}
Altaroth are usually found in groups of three to five, though they form large communities of up to a hundred individuals all living together in a huge nest. When encountered in the wild, a worker group is usually escorted by at least one soldier, though they will not attack if not disturbed. The distinction between the types is not believed to be a genetic difference, but a result of special food when young. This allows the hive to breed the type of Altaroth that is needed whenever it is required. It is also suspected that an Altaroth hive is somehow connected, with the individuals receiving orders remotely, perhaps from some kind of king or queen individual. However, there is no confirmed sighting of such a specimen.

Hunters and gatherers often find Altaroth useful because one can easily tell the existence and type of nearby resources by the color of their abdomens. Some herbalists and alchemists also attest special properties to the digested nutrients the Altaroth carry. Unprocessed, this substance is not edible.

\subsubsection{Carves}
Like with many insects, the best way to make sure that anything salvageable remains of a slain Altaroth is to use poison, as otherwise it might break and nothing useful remains.

\begin{hbNarrowTable}{Altaroth Carves}{RY}
\textbf{d100} & \textbf{Carve}\\
01-50 & \tableicon{sac-slime} Altaroth Stomach\\
51-75 & \tableicon{potion-cyan} Monster Fluid\\
76-100 & \tableicon{claw-slime} Altaroth Jaw
\end{hbNarrowTable}

\begin{hbNarrowTable}{Altaroth Abdomen Content}{RY}
\textbf{d100} & \textbf{Carve}\\
01-45 & \tableicon{mushroom-cyan} Ripened Mushroom\\
46-90 & \tableicon{potion-blue} Monster Broth\\
91-100 & \tableicon{webbing-orange} Honey
\end{hbNarrowTable}

\monsterheader{assets/ext/icons/anteka}{Anteka}{\FiveStarOpen}{No Stars}
\textit{Small herbivores known for their gentle demeanour as well as medicinal properties of their horns. Those wishing to harvest a horn should stun the Kelbi with blunt attacks and then sever it while the animal is still alive.}

\monsterheader{assets/ext/iconsL/arzuros}{Arzuros}{\FiveStar\FiveStar}{2 Stars}
\textit{Forest- and mountain-dwelling beasts found in humid regions. Though known more for fishing and standing upright to collect honey, their thick claws and heavy forearm plating allow them to deliver powerful blows to any aggressor.}\sizecrowns{501}{854}
\subsubsection{Physiology \& Ecology}
Arzuros is a four-legged omnivorous beast with an ursine body structure. Particularly notable are its particularly strong and dextrous forelegs as well as the armor plating covering its head, upper back and arms.



\subsubsection{Behaviour}

\subsubsection{Carves}

\monsterheader{assets/ext/iconsL/bnahabra}{Bnahabra}{\FiveStarOpen}{No Stars}
\textit{Pervasive flying insects that attack invaders with paralyzing venom and lay eggs in carrion along with a fluid that hastens decomposition. It is best to kill them with poison so that their parts are left ripe for the carving.}
%\subsubsection{Physiology \& Ecology}
%Test
%\subsubsection{Behaviour}
%Test
%\subsubsection{Carves}
%Test

\monsterheader{assets/ext/icons/moofah}{Moofah}{\FiveStarOpen}{No Stars}
\textit{Small herbivores that can be found on the Deserted Island. Their soft, high-quality fur has been used since ancient times in clothing and ceremonial tools, and can be shaved off of them with cutting weapons. They are docile and raised as livestock in many regions.}

\monsterheader{assets/ext/icons/rajang}{Rajang}{\FiveStar\FiveStar\FiveStar\FiveStar\FiveStar\FiveStar\FiveStar\FiveStar}{8 Stars}
\textit{An ultra-aggressive creature that is rarely sighted and seldom survived. Survivors report it exhibits a strange attack. The Rajang is said to be a loner, and this isolated life has made it difficult to pin down its territorial leanings.}

\section{Brute Wyverns}
In addition to regular brute wyverns, there are also pseudo-wyverns in this category\hbNone whereas true brute wyverns walk only on their hind legs, pseudo-wyverns in this category walk on four legs but also don't have wings.

\monsterheader{assets/ext/icons/aptonoth}{Aptonoth}{\FiveStarOpen}{No Stars}
\textit{Relatively docile herbivores with characteristic crest plates. They form herds and raise young communally, and have been used as pack animals for generations. Their meat is tasty and nutritious, and they're very cautious around large monsters.}

\monsterheader{assets/ext/iconsL/deviljho}{Deviljho}{\FiveStar\FiveStar\FiveStar\FiveStar\FiveStar\FiveStar\FiveStar}{7 Stars}
\textit{The dreaded, nomadic Deviljho have no specific territory of their own. Their muscles swell if provoked, revealing old wounds. They need to feed constantly due to high body heat and can hunt nearby animals to extinction.}

\monsterheader{assets/ext/icons/larinoth}{Larinoth}{\FiveStarOpen}{No Stars}
\textit{These giant herbivores are peaceful towards hunters unless their young are threatened. Their long necks let them eat hard-to-reach leaves and nuts, which they may drop if attacked while feeding, and eat constantly to maintain their size. They also have a unique sound-producing organ.}

\section{Bird Wyverns}
Bird wyverns are characterised by their bipedal stance and slender build. Many species of bird wyvern have developed wings and are capable of flight. Those that can fly are sometimes referred to as \emph{true bird wyverns} and those that cannot as \emph{pseudo bird wyverns}.

\monsterheader{assets/ext/icons/gargwa}{Gargwa}{\FiveStarOpen}{No Stars}
\textit{Fightless, plain-dwelling bird wyverns with vestigial wings. Quite timid, Gargwa have been known to lay eggs when other creatures surprise them from behind. They are raised as livestock in numerous villages.}

\monsterheader{assets/ext/icons/jaggi}{Jaggi}{\FiveStar}{One Star}
\textit{Highly social, carnivorous bird wyverns that live in large packs. Young Jaggi males hunt in groups when attacking larger animals and have been known to steal wyvern eggs. Research suggests they operate under orders from a single alpha male.}

\monsterheader{assets/ext/icons/velociprey}{Velociprey}{\FiveStar}{One Star}
\textit{Aggressive, carnivorous monsters that often travel and hunt in packs\hbNone even master hunters are careful to not let themselves get surrounded by these predators.}

\monsterheader{assets/ext/icons/genprey}{Genprey}{\FiveStar}{One Star}
\textit{Bird wyverns with a distinctive green-and-orange striped hide, Genprey live in packs in the Dunes and Primal Forest. Their claws and large fangs contain a paralyzing neurotoxin that they use to stun prey.}

\monsterheader{assets/ext/icons/ioprey}{Ioprey}{\FiveStar}{One Star}
\textit{A vivid red species of small carnivores often found in subtropical zones. Sacs in their throats contain a powerful poison that slowly drains the Health of their prey.}

\monsterheader{assets/ext/icons/giaprey}{Giaprey}{\FiveStar}{One Star}
\textit{A species of small bird-like carnivores known to inhabit the snowy mountains. Their white skin is beautiful, but their temperament is not. They are known to spit ice at hunters, and attack in deadly packs.}

\monsterheader{assets/ext/icons/velocidrome}{Velocidrome}{\FiveStar\FiveStar}{2 Stars}
\textit{Alpha monsters that lead Velociprey packs. Larger than their brothers and with a more prominent crest, Velocidrome use their strong hind legs to leap at prey, pinning them with sharp claws before calling for others.}\sizecrowns{590}{1,736}

\monsterheader{assets/ext/icons/gendrome}{Gendrome}{\FiveStar\FiveStar}{2 Stars}
\textit{Alpha monsters that lead Genprey packs. Larger than their brothers and with a more prominent crest, Gendrome use the venom in their highly evolved fangs and claws to paralyze their prey.}\sizecrowns{615}{1,037}

\monsterheader{assets/ext/icons/iodrome}{Iodrome}{\FiveStar\FiveStar}{2 Stars}
\textit{Alpha monsters that lead Ioprey packs. Larger than their brothers and with a more prominent crest, Iodrome spit a poison that slowly saps the life from their prey. They are found primarily in subtropical zones.}\par\sizecrowns{619}{1,641}

\monsterheader{assets/ext/iconsL/giadrome}{Giadrome}{\FiveStar\FiveStar}{2 Stars}
\textit{The alpha leader of a pack of Giaprey, the Giadrome sports a beautiful crest. Larger than a Giaprey, any hunter silly enough to encroach on its turf will be frozen in a hail of ice.}\sizecrowns{649}{959}

\subsubsection{Physiology \& Ecology}
Velociprey are two-legged pack hunters who rely on their high speed and long claws, as well as strength in numbers to take down prey\hbNone usually young Aptonoth. Their slender build identifies them as a bird wyvern, even though their lack of wings places them in the category of pseudo bird wyverns. Notable across all species of Velociprey are the prominent crests, which are present in both sexes and play an important role in determining the pack order.

For attack, Velociprey rely on their unusual, seven-clawed hands as well as their razor-sharp teeth. The teeth in particular are fused with the beak and are extremely hard, withstanding even gunpowder blasts. They have great mobility, owing to their strong hind legs, which also allow them to make leaping attacks and retreats.

The leader of the pack, the Velocidrome is the individual with the largest crest. On Velocidrome, the midle hand claw as well as the foot claws are particularly developed. As a result, it uses leaping attacks far more aggressively than its subordinate brethren.

Many species of Velociprey have developed in different biomes. Some have developed venom, which is either spat at prey or delivered via the claws. Between them, the many related species of Velociprey inhabit practically every biome on the planet and are an ever-present danger when venturing out into the wilderness. In many areas, a Velociprey attack is a far more realistic risk than an attack by a flying wyvern.

While they compete for prey with Jaggi, they have found different solutions to the same evolutionary problem: Velociprey are about speed, whereas Jaggi develop for raw strength. In addition, Velociprey are more intelligent than Jaggi, whereas Jaggi are more social.

\subsubsection{Behaviour}
Unless when intruding on their nest, Velociprey will usually not attack humanoids unless they are desperate. The issue of Velociprey perfectly illustrate why the Guild must exist: Whenever Velociprey attack a village, a disturbance in the ecosystem can be made directly responsible, as that is not their normal behaviour. If hunting were not the carefully monitored activity that it is, such attacks would be far more common.

When cornering prey, Velociprey coordinate effectively, communicating with surprising efficacy through calls. Whenever possible, they will keep their distance and tire out their prey before going in for the kill, though they are more than well-equipped for an encounter in close quarters. It is likely that one encounters the Velocidrome first, as it constantly patrols the area sorrounding the pack's nest, looking for prey and intruders. If it is not already escorted, it will quickly call for reinforcements before taking on the would-be nest robber. The crest is the Velocidrome's symbol of power, if it is broken, it will lose its authority in the pack, possibly even leading to infighting to determine the new pack alpha.

Like many small predators, Velociprey are afraid of fire.

\begin{hbNarrowTable}{Velociprey Body Carves}{RY}
\textbf{d100} & \textbf{Carve}\\
01-42 & \tableicon{claw-blue} Velociprey Fang$\times$1d4\\
43-75 & \tableicon{scale-blue} Velociprey Scale$\times$1d4\\
76-100 & \tableicon{hide-blue} Velociprey Hide\\
\end{hbNarrowTable}

\begin{hbNarrowTable}{Velocidrome Body Carves}{RY}
\textbf{d100} & \textbf{Carve}\\
01-53 & \tableicon{claw-blue} Velocidrome Claw\\
54-84 & \tableicon{hide-blue} Velocidrome Hide\\
85-96 & \tableicon{scale-blue} Velocidrome Scale\\
97-100 & \tableicon{hide-blue} Bird Wyvern Gem\\
\end{hbNarrowTable}

\begin{hbNarrowTable}{Wound Velocidrome Head}{RY}
\textbf{d100} & \textbf{Carve}\\
01-40 & \tableicon{claw-blue} Velocidrome Fang$\times$1d4\\
41-90 & \tableicon{sac-grey} Screamer Sac, \tableicon{claw-blue} Velocidrome Fang$\times$1d4\\
91-100 & \tableicon{carapace-blue} Velocidrome Head\\
\end{hbNarrowTable}
Other species use the same distribution for their respective claws, hides, fangs, scales and hides. Swap \tableicon{sac-grey}~Screamer Sac with \tableicon{sac-yellow}~Paralysis Sac for Gendrome, \tableicon{sac-purple}~Poison Sac for Iodrome and \tableicon{sac-cyan}~Frost Sac for Giadrome.


\section{Flying Wyverns}
True wyverns have a heavier build than bird wyverns and all species have at some point developed wings. Contrary to what the name would have you believe, not all flying wyverns can fly. In some species, the wingarms have regressed to being forearms again.

\monsterheader{assets/ext/icons/khezu}{Khezu}{\FiveStar\FiveStar\FiveStar\FiveStar}{4 Stars}
\textit{Loathsome wyverns that dwell in caves and other dark places. All but blind, Khezu hunt by smell, using electric shocks to paralyze their prey before pouncing on them from the walls or ceiling.}\sizecrowns{436}{1,225}
\subsubsection{Physiology \& Ecology}
For many years, Khezu was considered a myth, a mysterious creature supposedly living underground, its body one long series of disgusting anomalies and a silent hunter to be afraid of. It was not until some time after the Guild was founded and information about monsters was shared in a more organised fashion that the facts about Khezu were seperated from the fantasies. It is true that it is an elusive wyvern, living in cold areas, nearly entirely underground and in complete darkness.

Its body has adapted in various ways to this environment: It's scaleless, rubbery skin is nearly translucent, appearing grey with visible blood vessels and is covered by a slimy mucus which, together with a layer of fat, helps to keep Khezu warm even when it is not moving. Its eyes have almost completely regressed, making it practically blind. Instead, it relies mainly on smell and hearing to locate predators and prey, which it does with great efficacy. It is suspected that Khezu also possesses an additional sense, owing to its electric organ, which allows it to sense nearby electrical disturbances.

Its scaleless skin and electricity producing organ are by far not the only strange features that set Khezu apart from other wyverns. It has a very flexible extending neck, which seemingly ends directly with its mouth with no discernible head. It often uses this neck to surprise prey in caves while it hangs from the ceiling using its suction tail, as well as holding on with four feet\hbNone the wingarms have hands with a little flexibility.

Becides its mouth full of crushing fangs, hunters should watch out for its saliva, which is highly acidic. It's not as strong as that of Deviljho, which has been known to eat through armor, but it is a threat nevertheless. It will also make frequent use of its ability to project electric shocks around it, while it itself is fully shielded from such effects thanks to its thick rubber skin.

Khezu is a hemaphrodite, meaning the same individual is both male and female. When reproducing, Khezu will paralyze a medium-sized monster, such as a Popo and lay its eggs inside the monster while it is still alive. The eggs are partially incubated before Khezu deposits them, so they will hatch quickly and the young, called whelps will have their first meal immediately. A whelp's mouth is actually underdeveloped at birth, making it unable to feed normally. It actually uses its tail to drain blood from prey until its mouth has fully developed.

Khezu is a migratory wyvern. For most of the year, it lives in cold and snowy areas, but during the winter it will move to somewhat warmer latitutes. It will always prefer to be underground and near running water. Water is believed to be necessary to keep its skin damp, similar to an amphibian. Staying underground has several advantages for Khezu: Outside, it is vulnerable to larger, more dangerous wyverns as well as handicapped by its lack of sight. Underground, it has the advantage due its superiour other senses and it can use the ceiling to attack from above. It is unclear whether Khezu can fly. The overall body structure is more similar to that of Tigrex than to Rathian, giving credibility to the theory that they can't. They certainly have very little cause to do so underground.

\subsubsection{Behaviour}
Khezu has had only limited contact with humanoids, as it lives far away from places where humans or wyverians build their villages. Lynians have actually had a great deal more contact with this wyvern than the other intelligent races. Because its biology was such a mystery, for a long time hunters would actually seek out the illustrious Khezu, considering it something of a cryptozoid.

The only occasions where one might see a Khezu above ground are during its migration or when the food in its habitat is seriously scarce. For the reasons above, Khezu itself prefers not to go outside. Even though that limits the threat it poses to society, it has been hunted semi-frequently (legally and illegally) since the confirmation of its existence. Khezu whelps are considered a delicacy, even though the monsters were almost certainly hunted without Guild permission, as Guild only very rarely posts quests for non-adult monsters. There is also a fluid harvested from a Khezu's body known as Pale Extract, which is used as part of many medicines, adding to the demand for Khezu parts.

Of course, we cannot condone the unsanctioned hunting of monsters and would-be poachers should certainly not make a mistake and consider Khezu an easy target. In its native habitat, Khezu can move in complete silence and will likely know of the hunters long before they know of it. It will then attempt to attack from a surprise position, hanging from the ceiling or hiding in a crack. Instead of committing to an open fight it will more likely retreat and attempt to find another advantageous location.

\begin{hbNarrowTable}{Body Carves}{RY}
\textbf{d100} & \textbf{Carve}\\
01-30 & \tableicon{carapace-white} Pale Steak, \tableicon{hide-white} Flabby Hide\\
31-50 & \tableicon{bone-white} Pale Bone, \tableicon{hide-white} Flabby Hide\\
51-75 & \tableicon{potion-white} Pale Extract$\times$2\\
76-90 & \tableicon{sac-yellow} Electro Sac\\
91-96 & \tableicon{carapace-white} Khezu Special Cut\\
97-100 & \tableicon{monster-jewel-blue} Large Wyvern Gem
\end{hbNarrowTable}

\begin{hbNarrowTable}{Wound Head}{RY}
\textbf{d100} & \textbf{Carve}\\
01-54 & \tableicon{hide-white} Flabby Hide\\
55-79 & \tableicon{potion-white} Pale Extract\\
80-94 & \tableicon{carapace-white} Pale Steak\\
95-100 & \tableicon{carapace-white} Khezu Special Cut
\end{hbNarrowTable}

\monsterheader{assets/ext/icons/rathian}{Rathian}{\FiveStar\FiveStar\FiveStar\FiveStar}{4 Stars}
\textit{Fire-breathing female wyverns, also known as the "Queens of the Land". With powerful legs and poison-secreting tails, they hunt mainly on the ground. Sometimes seen preying as a couple, Rathians and Rathalos cooperate well.}

\monsterheader{assets/ext/icons/tigrex}{Tigrex}{\FiveStar\FiveStar\FiveStar\FiveStar\FiveStar\FiveStar}{6 Stars}
\textit{Flying wyverns whose primitive origins are obvious. Prone to violence, they display incredible ferocity with their claws, jaws, and developed limbs. They inhabit a wide area searching for prey, and have even been spotted in regions of harsh cold.}\sizecrowns{1,388}{2,603}
\subsubsection{Physiology \& Ecology}
Tigrex is considered by many to be the original flightless flying wyvern and a prime example of how the wingarms of some species of wyverns have regressed to forearms, giving Tigrex very good maneuverability and speed on the ground. Another distinctive feature is its yellow and cyan striped coloring, which can light up red when Tigrex is fighting with all its strength. Its wingspan is not sufficient to allow Tigrex to fly, but the webbing, combined with its high jumping strength, allows it to travel relatively long distances by gliding. When charging, it can accelerate to speeds of up to 50\,km/h, leading into either a massive slam with its forearms or a bite from its fearsome maw. From a running start, Tigrex is capable of making astonishing leaps. Many a hunter has thought themselves in a safe position, only for Tigrex to demonstrate that they were very much not out of reach. Like other wyverns, Tigrex is capable of walking on only its hind legs and will assume this stance when not in combat.

Tigrex prefers areas with cliffs and crevices that it can use as ramps to swoop down on prey or corner its quarry. It is very adaptable to different climates and has been spotted in areas ranging from deserts to glaciers, though it prefers warmer climate, only seeking out cold areas to hunt its favourite food: Popo. Tigrex has impressive stamina. It is able to stalk prey for days while using very little energy. Among hunters, it is more well known for the all-out hyper-aggressive fighting style it will assume when in combat, which will leave it quickly exhausted and hungry.

Another weapon in Tigrex' arsenal is its unique roar. Rather than being a high-pitched warning sound like for other wyverns, it is a weapon in its own right. With its roar alone, Tigrex is able to shatter rocks and blow away nearby monsters and hunters. The roar is always preceeded by a huge inhale, giving a hunter just enough warning to drop to the ground and cover their ears, or suffer Tigrex' projected wrath.

\subsubsection{Behaviour}
Tigrex is not territorial. It wanders the land in search of prey and will knowingly enter another wyvern's turf. Most other wyverns will not challenge it while it is in their territory, because they (rightly) fear it. Until it feels genuinely threatened, Tigrex will attempt to use as little energy as possible, adopting a stalking hunting style. In this way, it chooses a target and then proceeds to pursue this target with a single-minded determination. When the prey has been cornered, it launches into its signature charge, instantly going from silent predator to maximum power. With Tigrex, there is usually no middle ground.

When stalking prey, Tigrex can sometimes be distracted, leaving it open for a suprise attack. When threatened, its first response is to roar. This alone is enough to cause most wyverns to flee. Before roaring, Tigrex will always assume a four-legged, stable stance, followed by the inhale. If it is unable to assume such a stance, because of restricted space or a restrained or injured forearm, it will not roar.

\begin{hbNarrowTable}{Body Carves}{RY}
\textbf{d100} & \textbf{Carve}\\
01-40 & \tableicon{scale-yellow} Tigrex Scale\\
41-77 & \tableicon{claw-yellow} Tigrex Claw\\
78-97 & \tableicon{shell-yellow} Tigrex Carapace\\
98-100 & \tableicon{mantle-yellow} Tigrex Mantle
\end{hbNarrowTable}
\begin{hbNarrowTable}{Tail Carves}{RY}
\textbf{d100} & \textbf{Carve}\\
01-97 & \tableicon{carapace-yellow} Tigrex Tail\\
98-100 & \tableicon{mantle-yellow} Tigrex Mantle, \tableicon{carapace-yellow} Tigrex Tail
\end{hbNarrowTable}
\begin{hbNarrowTable}{Wound Head}{RY}
\textbf{d100} & \textbf{Carve}\\
01-40 & \tableicon{shell-yellow} Tigrex Carapace\\
41-60 & \tableicon{shell-yellow} Tigrex Carapace, \tableicon{claw-yellow} Tigrex Fangs$\times$2d4 \\
61-92 & \tableicon{carapace-yellow} Tigrex Scalp, \tableicon{claw-yellow} Tigrex Fangs$\times$2d4\\
93-100 & \tableicon{shell-yellow} Tigrex Carapace, \tableicon{carapace-yellow} Tigrex Maw
\end{hbNarrowTable}
\begin{hbNarrowTable}{Wound Forearm}{RY}
\textbf{d100} & \textbf{Carve}\\
01-50 & \tableicon{claw-yellow} Tigrex Claw$\times$1d4\\
51-97 & \tableicon{shell-yellow} Tigrex Carapace, \tableicon{claw-yellow} Tigrex Claw$\times$1d4\\
98-100 & \tableicon{mantle-yellow} Tigrex Mantle, \tableicon{claw-yellow} Tigrex Claw$\times$1d4
\end{hbNarrowTable}

\section{Leviathans}
Leviathans are aquatic or at least partially aquatic predators. Like wyverns on land, they are typically the top of the food chain in the environment they are found in. Some Leviathans have developed the ability to swim in sand instead of water and are particularly adapted towards that environment, though they often have similar behaviour to their aquatic cousins.

\monsterheader{assets/ext/iconsL/delex}{Delex}{\FiveStar}{1 Star}
\textit{Carnivorous desert monsters that travel in schools of four or five. Delex often follow large predators in the hope of scavenging leftovers, and have even been known to hitch rides on hunting sandskiffs. They are extremely sensitive to sound.}

\monsterheader{assets/ext/iconsL/fish}{Fish}{\FiveStarOpen}{No Stars}
\textit{This category includes carnivorous fish (Sharq, Catfish), migratory fish (Tuna, Arowanas), and natatorial fish (Molids, Perciformes). Fish often flee when attacked, so hunters prefer to use harpoons to obtain materials from them.}

\monsterheader{assets/ext/icons/ludroth}{Ludroth}{\FiveStar}{1 Star}
\textit{Aquatic female monsters. Ludroth form "harems" around large males, gathering in territories designated as breeding grounds. They're known to be extremely aggressive towards outsiders, so caution is advised when treading in their territory.}

\monsterheader{assets/ext/icons/plesioth}{Plesioth}{\FiveStar\FiveStar\FiveStar}{3 Stars}
\textit{Giant piscine wyverns which can be spotted near bodies of water. Where wings would be found on other wyverns, it has developed fins specialized for swimming, and, as a result, cannot fly. Despite its fish-like appearance, it is just as comfortable on land.}

\section{Elder Dragons}
The greatest and most ancient force among the monsters are the Elder Dragons. A single one can pose a threat to even the larger cities of the world and Dundorma has actually been destroyed by one several times. Being the awesome forces that they are, it is no surprise that they are represented in many songs and myths.

Biologically speaking, not much is known about the Elder Dragons, as there is no known event of one being killed (and thus studied). In some cases (such as Kirin), the label "Elder Dragon" is simply attached to a monster that fits no other categorisation and is not considered definitive. It is not known whether the Elder Dragons each represent a whole species or are unique individuals.

The Guild sees all Elder Dragons as threats that must be eliminated, but there is evidence that in the past, Elder Dragons were revered as gods, and some such cults continue to exist today.

So little is known with certainty about the Elder Dragons that we are not even sure if the creatures listed here are individuals or whole species. A first step to finding this out would be successfully slaying one. As this has never been accomplished, we cannot be sure.

\monsterheader{assets/ext/iconsL/jhen-mohran}{Jhen Mohran}{\FiveStarOpen}{unrated}
\textit{Rare ore can be mined from this enormous dragons' back; thus it is considered a prosperity symbol. It swallows vast amounts of organic material and is always surrounded by scavenging Delex, which sailors use to locate it.}

\monsterheader{assets/ext/icons/kirin}{Kirin}{\FiveStarOpen}{unrated}
\textit{Elder dragon so rarely sighted that little is known of its ecology. It's been said it is one with lightning itself, and that its body becomes clothed in pure electricity when it is provoked.}

\monsterheader{assets/ext/icons/kushala-daora}{Kushala Daora}{\FiveStarOpen}{unrated}
\textit{A metal plated dragon known as the tempest of wind. Eyewitnesses report violent storms alongside the dragon, and its wide range means towns may be attacked.}

\monsterheader{assets/ext/iconsL/lao-shan-lung}{Lao-Shan Lung}{\FiveStarOpen}{unrated}
\textit{A giant dragon few have seen and lived to tell the tale. When on the rampage it wreaks havoc on all in its path.}

\monsterheader{assets/ext/icons/fatalis}{Fatalis}{\FiveStarOpen}{unrated}
\textit{Stories of this legendary dragon date back to antiquity. Many skilled hunters have sought to challenge it, but none have ever returned. A monster shrouded in mystery\ldots}

\vspace{8pt}{\centering
{\color{chapter}\LARGE\mreaves The Legend of the Black Dragon}\\[4pt]
\itshape
When the world is full of wyverns\\
The legend is revived\\
Meat is eaten, Bone is crunched.\\
And blood is sucked up dry\\[6pt]

He burns the earth\\
And melts through iron\\
He boils the rivers\\
And mows down trees\\
He awakens the winds\\
And lights an inferno\\[6pt]

He is called Fatalis\\
The wyvern of destiny\\
He is called Fatalis\\
The wyvern of destruction\\
Call for help\\
Run for your lives\\
And don't forget to\\
Pray to the skies\\[6pt]

He is called Fatalis\\
The wyvern of destiny\\
He is called Fatalis\\
The wyvern of destruction\\
Fatalis, Fatalis\\
Heaven and Earth are yours\\
Fatalis, Fatalis\\
Heaven and Earth are yours\\}
